Lesson 5
========================================================

### Multivariate Data
```{r}
pf <- read.delim('../lesson3/pseudo_facebook.tsv')
```

***

### Moira Perceived Audience Size Colored by Age
```{r}
library(ggplot2)

qplot(x = friend_count, data = na.omit(pf), binwidth = 10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)
```

***

### Third Qualitative Variable
```stat = "identity"``` 使ggplot直接取用count欄位當成高度，不用再數資料的個數。

```{r Third Qualitative Variable}
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + 
  geom_histogram(stat = "identity")
  # geom_bar(stat = "identity")

ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + 
  geom_boxplot() + 
  stat_summary(fun.y = mean, geom = "point", shape = 4)  # 標記平均值

ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(gender))) + 
  geom_line(aes(color = gender), stat = "summary", fun.y = median)
```

```{r}
suppressMessages(library(dplyr))

# chain functions together %>%
pf.fc_by_age_gender <- pf %>% 
  filter(!is.na(gender)) %>%   # or use subset(pf, !is.na(gender))
  group_by(age, gender) %>%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n()) %>%
  ungroup() %>%
  arrange(age)

head(pf.fc_by_age_gender)
```

***

### Plotting Conditional Summaries

```{r Plotting Conditional Summaries}
ggplot(aes(x = age, y = median_friend_count), 
           data = pf.fc_by_age_gender) + 
  geom_line(aes(color = gender))
```

***

### Reshaping Data

```{r Reshaping Data}
# install.packages("tidyr")
library(tidyr)
spread(subset(pf.fc_by_age_gender,
              select = c('gender', 'age', 'median_friend_count')),
       gender,
       median_friend_count)
```

```dcast()```: Convert long format to wide format
```melt()```: Convert the Y data back to the original long format

```{r Reshaping Data}
# install.packages('reshape2')
library(reshape2)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = "median_friend_count")
head(pf.fc_by_age_gender.wide)
```

```{r Ratio}
subset(pf.fc_by_age_gender[c('age', 'gender', 'median_friend_count')],
       !is.na(gender)) %>%
  spread(gender, median_friend_count) %>%
  mutate(ratio = female / male)
```

***

### Ratio Plot

```{r Ratio Plot}
ggplot(aes(x = age, y = female / male),
       data = pf.fc_by_age_gender.wide) + 
  geom_line() + 
  geom_hline(yintercept = 1, alpha = 0.5, linetype = 2) # 截距(yintercept)為1
```

***

### Third Quantitative Variable
```floor()```: 無條件捨去
```ceiling()```:  無條件進位

```{r Third Quantitative Variable}
pf$year_joined <- floor(2014 - pf$tenure / 365)
```

***

### Cut a Variable

```cut()``` 對於從連續或數值變量建立離散變量時非常有用，有時會與分位數函數結合。

```{r Cut a Variable}
summary(pf$year_joined)
table(pf$year_joined)

pf$year_joined.bucket <- cut(pf$year_joined,
                             breaks = c(2004, 2009, 2011, 2012, 2014))
table(pf$year_joined.bucket, useNA = "ifany")
```

***

### Plotting it All Together

```{r Plotting it All Together}
ggplot(aes(x = age, y = friend_count), 
              data = subset(pf, !is.na(year_joined.bucket))) + 
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = median)
```

***

### Plot the Grand Mean

```{r Plot the Grand Mean}
ggplot(aes(x = age, y = friend_count), 
              data = subset(pf, !is.na(year_joined.bucket))) + 
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean) + 
  geom_line(stat = 'summary', fun.y = mean, linetype = 2)
```

***

### Friending Rate

```{r Friending Rate}
with(subset(pf, tenure >= 1),         # 至少註冊一天的用戶
     summary(friend_count / tenure))  # 每天的好友數
```

***

### Friendships Initiated

```{r Friendships Initiated}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) + 
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)
```

***

### Bias-Variance Tradeoff Revisited
將ggplot的```x = tenure```替換為```x = 7 * round(tenure / 7)```等，通過```round()```的分母將數值分箱，然後轉換回前面帶有常量的自然標尺。

```{r Bias-Variance Tradeoff Revisited}
p1 <- ggplot(aes(x = tenure, y = friendships_initiated / tenure),
             data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

p2 <- ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
             data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

p3 <- ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
             data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

p4 <- ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
             data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

library(gridExtra)
grid.arrange(p1, p2, p3, p4, ncol = 1)
```

```{r Bias-Variance Tradeoff Revisited}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) + 
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean) + 
  geom_smooth()

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) + 
  geom_smooth(aes(color = year_joined.bucket))
```

***

### Introducing the Yogurt Data Set

```{r}
read.delim('../lesson5/yogurt.tsv')
```

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}

```

***

### Prices over Time
Notes:

```{r Prices over Time}

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***