---
title: "Udacity: Data Analysis with R - Problem Set 3"
output: html_notebook
---

# Data Analysis with R by Facebook

## Explore One Variable Problem Set

### Import ggplot2 and diamonds data set

```{r}
library(ggplot2)
data(diamonds)
?diamonds
```

### Basic exploration of data set

```{r}
View(diamonds)
str(diamonds)
summary(diamonds)
```

### Histogram of the price of all the diamonds

```{r}
str(diamonds$price)
summary(diamonds$price)

qplot(x = price, data = diamonds)

ggplot(aes(x = price), data = diamonds) +
   geom_histogram(color = 'black', fill = '#099DD9')
```

```{r}
# How many diamonds cost less that $500 ?
summary(diamonds$price < 500)
dim(subset(diamonds, price < 500))
nrow(subset(diamonds, price < 500))

# How many diamonds cost less than $250 ?
summary(diamonds$price < 250)
dim(subset(diamonds, price < 250))
nrow(subset(diamonds, price < 250))

# How many diamonds cost $15000 or more ?
summary(diamonds$price >= 15000)
dim(subset(diamonds, price >= 15000))
nrow(subset(diamonds, price >= 15000))
```


### Explore the largest peak in the price histogram

Try limiting the x-axis, altering the bin width, and setting different breaks on the x-axis.

There won’t be a solution video for this question so go to the discussions to share your thoughts and discover what other people find.

```{r}
qplot(x = price , data = diamonds, 
      binwidth = 250,
      color = I('black'), fill = I('#099DD9'),
      xlab = 'Price of Diamonds',
      ylab = 'Count of Diamonds') +
  scale_x_continuous(limits = c(250,19000), breaks = seq(0,19000, 1000))

ggplot(aes(x = price), data = diamonds) + 
  geom_histogram(binwidth = 250,
                 color = "black", fill = "#099DD9") +
  coord_cartesian(xlim=c(250,19000)) + 
  scale_x_continuous(breaks = seq(0,19000, 1000)) + 
  ggtitle("Diamonds Price")
```

You can save images by using the ggsave() command.
```ggsave()``` will save the last plot created.
ggsave currently recognises the extensions eps/ps, tex (pictex), pdf, jpeg, tiff, png, bmp, svg and wmf (windows only).

```{r}
ggsave()
```


### Histogram of diamond prices by cut.

Facets (ggplot2)
http://www.cookbook-r.com/Graphs/Facets_(ggplot2)/

```{r}
qplot(x = price , data = diamonds, 
      binwidth = 500,
      color = I('black'), fill = I('#099DD9'),
      xlab = 'Price of Diamonds',
      ylab = 'Count of Diamonds') +
  scale_x_continuous(limits = c(250,20000), breaks = seq(0,20000, 5000)) +
  facet_wrap( ~ cut)

ggplot(aes(x = price), data = diamonds) + 
  geom_histogram(binwidth = 500,
                 color = "black", fill = "#099DD9") +
  coord_cartesian(xlim=c(250,20000)) + 
  scale_x_continuous(breaks = seq(0,20000, 5000)) + 
  ggtitle("Diamonds Price") +
  facet_grid(. ~ cut)
```


### Price by Cut

```{r}
by(diamonds$price, diamonds$cut, summary)
# by(diamonds$price, diamonds$cut, summary, digits = max(getOption('digits')))

# Which cut has the highest priced diamond ?
max(by(diamonds$price, diamonds$cut, max))
# Premium

# Which cut has the lowest priced diamond ?
min(by(diamonds$price, diamonds$cut, min))
# Premium, Ideal

# Which cut has the lowest median price ?
min(by(diamonds$price, diamonds$cut, median))
# Ideal
```

Then, scroll back up and add a parameter to facet_wrap so that the y-axis in the histograms is not fixed. You want the y-axis to be different for each histogram.

```{r}
qplot(x = price, data = diamonds,
      binwidth = 500,
      color = I('black'), fill = I('#099DD9')) +
  facet_wrap( ~ cut, scales = "free_y")
```


### Histogram of price per carat by cut.

You can make adjustments to the code from the previous exercise to get started.
Adjust the bin width and transform the scale of the x-axis using log10.

```{r}
qplot(x = log10(price/carat), data = diamonds,
      binwidth = 0.05,
      color = I('black'), fill = I('#099DD9')) +
  facet_wrap( ~ cut, scales = "free_y")

ggplot(aes(x = price / carat), data = diamonds) + 
  geom_histogram(binwidth = 0.05,
                 color = "black", fill = "lightblue") +
  scale_x_log10() +
  facet_grid(. ~ cut)
```






