Lesson 3
Analyzing One Variable
========================================================

***

### What to Do First?

#### Reading in Data

```{r}
getwd()
list.files()
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

# read.delim()函數默認使用製表符作為值之間的分隔符，並使用句點作為十進製字符。
pf <- read.delim('pseudo_facebook.tsv')
```

***

### Pseudo-Facebook User Data

```{r Pseudo-Facebook User Data}
names(pf)
```

***

### Histogram of Users' Birthdays

```{r Histogram of Users\' Birthdays}
# install.packages('ggplot2')
library(ggplot2)

qplot(x = dob_day, data = pf)

qplot(x = dob_day, data = pf) + 
  scale_x_continuous(breaks = 1:31) +
  theme(text = element_text(size=10))

# scale_x_discrete() 圖層從 ggplot2 2.0 開始被棄用。改用 scale_x_continuous() 獲得斷點。
# theme() 設定文字大小
```

Notes: 
很多網站在註冊帳號時會將你的生日默認為1號，甚至1月1號。對於Facebook，他們的默認是1月1日。
探索數據時，留心這樣的細節非常重要。

```{r ggthems}
# install.packages('ggthemes', dependencies = TRUE)
library(ggthemes)

ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  theme_minimal() +
  theme(text = element_text(size=10))

# theme_minimal() 字體大小為24
ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  theme_set(theme_minimal(24)) +
  theme(text = element_text(size=10))
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
facet_wrap(~variable)
facet_grid(vertical ~ horizontal)

```{r Faceting}
qplot(x = dob_day, data = pf) + 
  scale_x_continuous(breaks = 1:31) + 
  facet_wrap(~dob_month, ncol = 3) +
  theme(text = element_text(size=10))

ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  facet_wrap(~dob_month) +
  theme(text = element_text(size=10))
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(x = friend_count, data = pf) +
  theme(text = element_text(size=10))

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() +
  theme(text = element_text(size=10))
```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes

```{r Limiting the Axes}
qplot(x = friend_count, data = pf, xlim = c(0, 1000)) +
  theme(text = element_text(size=10))

qplot(x = friend_count, data = pf) + 
  scale_x_continuous(limits = c(0, 1000)) +
  theme(text = element_text(size=10))

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() + 
  scale_x_continuous(limits = c(0, 1000)) +
  theme(text = element_text(size=10))
```

### Exploring with Bin Width
Notes: 組距默認超過30的範圍
```stat_bin()``` using ```bins = 30```. Pick better value with ```binwidth```

***

### Adjusting the Bin Width
```{r Adjusting the Bin Width}
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))

qplot(x = friend_count, data = pf, binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

### Faceting Friend Count

```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# facet_grid()，句點代表數據集中的其他所有變量，這一符號實質上根據性別拆分數據，並且生成三個直方圖，每個圖都有自己的行。

qplot(x = friend_count, data = pf, binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) + 
  facet_grid(.~gender)

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)
```

***

### Omitting NA Values

```{r Omitting NA Values}
# 去除所有性別變量為NA的值
qplot(x = friend_count, data = subset(pf, !is.na(gender)),
       binwidth = 10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)

qplot(x = friend_count, data = subset(pf, !is.na(gender)),
       bins = 200) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)

ggplot(aes(x = friend_count), data = subset(pf, !is.na(gender))) + 
  geom_histogram(binwidth = 10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)

ggplot(aes(x = friend_count), data = subset(pf, !is.na(gender))) + 
  geom_histogram(bins = 200) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)
```

```{r Omitting NA Values}
# na.omit()會去掉所有含有NA的值
qplot(x = friend_count, data = na.omit(pf), binwidth = 10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)
```

***

### Statistics 'by' Gender

```{r Statistics \'by\' Gender}
table(pf$gender)

# by()有三個輸入，變量或類別變量、劃分子集的指標列表以及函數
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure

```{r Tenure}
# 參數 color 決定了圖中對象的輪廓線顏色（color outline）
# 參數 fill 決定了圖中對象內的區域（area）顏色
# I() 函數代表“現狀”，並且告訴 qplot 將它們用作顏色。
# 合理的設定 binwidth = 30，因為30大概是一個月
qplot(x = tenure, data = pf, binwidth = 30,
      color = I('black'), fill = '#099DD9')

ggplot(aes(x = tenure), data = pf) +
   geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x = tenure/365, data = pf, binwidth = .25,
      color = I('black'), fill = I('#F79420'))

qplot(x = tenure/365, data = pf, binwidth = .25,
      color = I('black'), fill = I('#F79420')) + 
  scale_x_continuous(lim = c(0, 7), breaks = seq(1, 7, 1))
#  scale_x_continuous(limits = c(0, 7), breaks = seq(1, 7, 1))

ggplot(aes(x = tenure/365), data = pf) +
  geom_histogram(binwidth = .25, color = 'black', fill = '#F79420')
```

***

### Labeling Plots

```{r Labeling Plots}
qplot(x = tenure/365, data = pf, binwidth = .25,
      xlab = 'Number of years using Facebook',
      ylab = 'Number of users in sample',
      color = I('black'), fill = I('#F79420')) + 
  scale_x_continuous(lim = c(0, 7), breaks = seq(1, 7, 1))

ggplot(aes(x = tenure / 365), data = pf) + 
  geom_histogram(binwidth = .25, color = 'black', fill = '#F79420') + 
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) + 
  xlab('Number of years using Facebook') + 
  ylab('Number of users in sample')
```

***

### User Ages

```{r User Ages}
# Find Max Age
max(pf$age)

qplot(x = age, data = pf, binwidth = 1,
      color = I('black'), fill = I('#5760AB')) + 
  scale_x_continuous(breaks = seq(0, 113, 5))

ggplot(aes(x = age), data = pf) + 
  geom_histogram(binwidth = 1, color = 'black', fill = '#5760AB') + 
  scale_x_continuous(breaks = seq(0, 113, 5))
```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes: 對 Facebook 數據使用變換變量的 lotta 方法，大多數的數據如好友數、按讚數、評論數、塗鴉牆等都是變量，稱為約束變量（engagement variables），它們都有很長的尾巴。也就是說，有些用戶的按讚數、評論數會比其他用戶高出一個量級。
在統計學中，我們稱為數據過度離散，通常要對這些值進行變換，才能看到標準偏差或量級，實際上就是在縮短尾巴。
我們可以通過取對數來變換此變量，使用自然對數、以2或10為底的對數，或者使用其他函數如平方根，這樣可以幫助我們更清晰地看清楚模式，不被長尾分散注意。
很多統計方法，如線性迴歸，都是基於常態分佈假設，通過對此變量取對數，可以將數據轉換，使其可能變成常態分佈或近似常態分佈。

```{r Transforming Data}
qplot(x = friend_count, data = pf)

summary(pf$friend_count)

summary(log10(pf$friend_count))
# 有些值為負無窮大，因為有些用戶的好友數為0，當取以10為底的0的對數時，值是未定義的，其極限為負無窮大。

# tenfold scale like the pH scale
summary(log10(pf$friend_count + 1))

summary(sqrt(pf$friend_count))
```

***

### Add a Scaling Layer

```{r Add a Scaling Layer}
# install.packages('gridExtra')
library(gridExtra)

# qplot()
p1 <- qplot(x = friend_count, data = pf)
p2 <- qplot(x = log10(friend_count + 1), data = pf)
p3 <- qplot(x = sqrt(friend_count), data = pf)

grid.arrange(p1, p2, p3, ncol = 1)


# ggplot()
p1 <- ggplot(aes(x = friend_count), data = pf) + geom_histogram()
p2 <- p1 + scale_x_log10()
p3 <- p1 + scale_x_sqrt()

grid.arrange(p1, p2, p3, ncol = 1)
```

```{r}
# x軸使用對數為單位
logScale <- qplot(x = log10(friend_count), data = pf)

# xlab = friend_count
countScale <- ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() + 
  scale_x_log10()

grid.arrange(logScale, countScale, ncol = 2)

qplot(x = friend_count, data = pf) + 
  scale_x_log10()
```

***

### Frequency Polygons

```{r Frequency Polygons}
p1 <- qplot(x = friend_count,
            data = subset(pf, !is.na(gender)),
           # xlab('Friend Count'),
           # ylab('Percentage of users with that friend count'),
            binwidth = 10) + 
  scale_x_continuous(lim = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)

p2 <- qplot(x = friend_count,
            y = ..count../sum(..count..),
            data = subset(pf, !is.na(gender)),
           # xlab('Friend Count'),
           # ylab('Percentage of users with that friend count'), 
            binwidth = 10, geom = 'freqpoly', color = gender) + 
  scale_x_continuous(lim = c(0, 1000), breaks = seq(0, 1000, 50))

grid.arrange(p1, p2, ncol = 1)

ggplot(aes(x = friend_count, y = ..count../sum(..count..)),
       data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count') + 
  ylab('Percentage of users with that friend count')

# ..density..
ggplot(aes(x = friend_count, y = ..density..),
       data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count') + 
  ylab('Percentage of users with that friend count')
```

***

### Likes on the Web
Notes: 使用頻數多邊形確定哪個性別在網頁上獲得的點讚數更多。

```{r Likes on the Web}
qplot(x = www_likes, data = subset(pf, !is.na(gender)),
      geom = 'freqpoly', color = gender) + 
  scale_x_log10()

ggplot(aes(x = www_likes), data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender)) + 
  scale_x_log10()


qplot(x = www_likes, data = subset(pf, !is.na(gender)),
      geom = 'freqpoly', color = gender) + 
  scale_x_continuous() + 
  scale_x_log10()

by(pf$www_likes, pf$gender, sum)
```

***

### Box Plots

```{r Box Plots}
# Histograms
qplot(x = friend_count,
      data = subset(pf, !is.na(gender)),
      binwidth = 25) + 
  scale_x_continuous(lim = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)

# Box Plots
qplot(x = gender,        # 類別變量
      y = friend_count,  # 連續變量
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot')

# 離群值位於中位數IOR的1.5倍之外
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(x = gender,
      y = friend_count,
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot',
      ylim = c(0, 1000))

qplot(x = gender,
      y = friend_count,
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot') + 
  scale_y_continuous(limits = c(0, 1000))

# The Best 
qplot(x = gender,
      y = friend_count,
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot') + 
  coord_cartesian(ylim = c(0, 1000))
```

***

### Box Plots, Quartiles, and Friendships

```{r Box Plots, Quartiles, and Friendships}
qplot(x = gender,
      y = friend_count,
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot') + 
  coord_cartesian(ylim = c(0, 250))

by(pf$friend_count, pf$gender, summary)

# 25%的女性好友數大於244人
```

#### On average, who initiated more friendships in our sample: men or women?
Response: women
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
qplot(x = gender, y = friendships_initiated,
      data = subset(pf, !is.na(gender)), geom = 'boxplot') + 
  coord_cartesian(ylim = c(0, 150))

by(pf$friendships_initiated, pf$gender, summary)
```

***

### Getting Logical

```{r Getting Logical}
summary(pf$mobile_likes)
# 用戶使用手機登陸的次數可能無關緊要，但是該用戶是否曾經使用過是重要的。
# 由summary得知中位數為4，意味有很多的0。

# 設置比較運算符，得知某個用戶是否實際登錄了
summary(pf$mobile_likes > 0)

mobile_check_in <- NA
# 如果用戶有登錄過設置為1，沒有則設為0
pf$mobile_check_in <- ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in <- factor(pf$mobile_check_in)

summary(pf$mobile_check_in)
# 約有64000人使用過手機登陸

sum(pf$mobile_check_in == 0) / length(pf$mobile_check_in)
sum(pf$mobile_check_in == 1) / length(pf$mobile_check_in)
```

***