Lesson 3
========================================================

***

### What to Do First?

#### Reading in Data

read.delim()函數默認使用製表符作為值之間的分隔符，並使用句點作為十進製字符。
```{r}
getwd()
list.files()
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')
pf <- read.delim('pseudo_facebook.tsv')
```

***

### Pseudo-Facebook User Data

```{r Pseudo-Facebook User Data}
names(pf)
```

***

### Histogram of Users' Birthdays

```{r Histogram of Users\' Birthdays}
# install.packages('ggplot2')
library(ggplot2)

qplot(x = dob_day, data = pf)

qplot(x = dob_day, data = pf) + 
  scale_x_continuous(breaks = 1:31) +
  theme(text = element_text(size=10))

```


```{r ggthems}
# install.packages('ggthemes', dependencies = TRUE)
library(ggthemes)

ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  theme_minimal() +
  theme(text = element_text(size=10))

ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  theme_set(theme_minimal(24)) +
  theme(text = element_text(size=10))
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting

facet_wrap(~variable)
facet_grid(vertical ~ horizontal)

```{r Faceting}
qplot(x = dob_day, data = pf) + 
  scale_x_continuous(breaks = 1:31) + 
  facet_wrap(~dob_month, ncol = 3) +
  theme(text = element_text(size=10))

ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  facet_wrap(~dob_month) +
  theme(text = element_text(size=10))
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(x = friend_count, data = pf) +
  theme(text = element_text(size=10))

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() +
  theme(text = element_text(size=10))
```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes

```{r Limiting the Axes}
qplot(x = friend_count, data = pf, xlim = c(0, 1000)) +
  theme(text = element_text(size=10))

qplot(x = friend_count, data = pf) + 
  scale_x_continuous(limits = c(0, 1000)) +
  theme(text = element_text(size=10))

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() + 
  scale_x_continuous(limits = c(0, 1000)) +
  theme(text = element_text(size=10))
```

### Exploring with Bin Width
Notes: 組距默認超過30的範圍
```stat_bin()``` using ```bins = 30```. Pick better value with ```binwidth```

***

### Adjusting the Bin Width
```{r Adjusting the Bin Width}
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))

qplot(x = friend_count, data = pf, binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.

qplot(x = friend_count, data = pf, binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) + 
  facet_grid(gender ~ .)

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)

```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}

```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}

```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}

```

***

### User Ages
Notes:

```{r User Ages}

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}

```

***


### Frequency Polygons

```{r Frequency Polygons}

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}

```


***

### Box Plots
Notes:

```{r Box Plots}

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!